---
title: "Axon Classification"
author: "Patrick"
date: "2023-12-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Summary

Goal: Generate a pipeline for classifying axons as new, survived, or branched for each animal. Then merge it with structural_master_cut:

* Class definitions;
    - Survived: Axons present in W2 following DSP4 or saline treatment. Calculated by taking the summated surface area of all axon segments present in W2
    - Branched: Axon branches from 'survived' axons. Calculated by subtracting the summated surface area of all axon segments whose center of mass lies within 5um of the center of a 'survived' segment from the summated surface area of all ibranched axon segments. ibranched axon segments are those whose center of mass lies within 5um of the center of mass of 'survived' axons + branched growth identified by eye.
    - New: Axon growth originating from outside of the visible region. Calculated by subtracting the summatated surface area of all ibranched segments from the summated total of all axon segments in the area.
    
* 14 rows, one for each of data collection (-2 through 24)
* Columns:
    - segment.total.sa: total surface area of all axon segments
    - norm.segment.total.sa: normalized total surface area of all axon segments
    - new.sa: surface area of new axon growth
    - norm.new.sa: normalized surface area of new axon growth
    - survived.sa: surface area of survived axon
    - norm.survived.sa: normalized surface area of survived axons
    - branch.sa: surface area of axon growth branched from survived axons
    - norm.branch.sa: normalized surface area of axon growth branched from survived axons

# Writing a function that loads in the data for each animal calculates the information required and loads it into a data frame

Currently the ibranched and survived csvs don't have area information in them, just distance between spots and surface IDs. We need to merge these with the surface area csvs based on the IDs and then delete all rows with NA in the 'Shortest Distance to Spots' column...or maybe if there is an NA at all

```{r}
# load test files 9022 W8 ibranched and Surfaces
w8_9022_branch <- read.csv("./Axon Classification/9022/ibranched/W8.csv", skip = 3)
w8_9022_branch
w8_9022_surfaces <- read.csv("./Axon Classification/9022/Surfaces/W8.csv", skip = 3)
w8_9022_surfaces
```
Join dataframes based on the ID column
```{r}
bound9022 <- merge(w8_9022_branch, w8_9022_surfaces, by = "ID")
bound9022
```

Generate 4 functions. Each will generate a data frame with containing information for each week:

1. segment.total_calc(): will calculate the total segmented surface area for each week
2. survived_calc(): will calculate the total survived surface area for each week
3. branch_calc(): will calculate the total branched surface area for each week
4. new_calc(): will calculate the total new axon growth for each week. 

## Total segmented surface area function
```{r}
# Input file path to subject folders for survived, branched, and all axon segments
segment.total_calc <- function(surfaces_folder) {
    # Retrieve list of all CSV files in the subject's folders
    csv_files_surfaces <- list.files(surfaces_folder)

    # Create a sequence of week numbers
    week_numbers <- seq(-2, 24, by = 2)
    
    # Iterate over the 'surfaces' week numbers adding the data to the subject's data frame
    for (week_number in week_numbers) {
    # Check if the CSV file for the week exists in survived_folder
        csv_file <- paste0("W", week_number, ".csv")
        if (file.exists(file.path(surfaces_folder, csv_file))) {
            # If the CSV file exists, load it
            weekly_surfaces <- read.csv(file.path(surfaces_folder, csv_file), skip = 3)
            
            # Calculate the sum of the 'Area' column
            segment.total_sa <- sum(weekly_surfaces$Area)
            
        } else {
        # If the CSV file does not exist, fill in the total.sa value with NA
            segment.total_sa <- NA
        }
        
        # Add the week and total.sa values to the subject's data frame
        subject_data <- rbind(subject_data, data.frame(week = week_number,
                                                       segment.total.sa = segment.total_sa))
    }
    # Return the subject's data frame
    return(subject_data)
}
```


```{r}
subject_data <- data.frame()
# Input the correct file path
survived_folder <- "./Axon Classification/9022/W2_spotcomp"
ibranched_folder <- "./Axon Classification/9022/ibranched"
surfaces_folder <- "./Axon Classification/9022/Surfaces"
subject_data <- segment.total_calc(surfaces_folder)
subject_data
```  

Looks good. Onto the next

## Survived function
```{r}
survived_calc <- function(survived_folder, surfaces_folder) {
    # Retrieve list of all CSV files in the subject's folders
    csv_files_survived <- list.files(survived_folder)
    csv_files_surfaces <- list.files(surfaces_folder)

    # Create a sequence of week numbers
    week_numbers <- seq(-2, 24, by = 2)

    # Iterate over the 'survived' week numbers adding the data to the subject's data frame
    for (week_number in week_numbers) {
    # Check if the CSV file for the week exists in survived_folder
        csv_file <- paste0("W", week_number, ".csv")
        if (file.exists(file.path(survived_folder, csv_file))) {
            # If the CSV file exists, load it
            weekly_survived <- read.csv(file.path(survived_folder, csv_file), skip = 3)
            weekly_surfaces <- read.csv(file.path(surfaces_folder, csv_file), skip = 3)
            weekly_survived <- merge(weekly_survived, weekly_surfaces, by = "ID")
            
            # Calculate the sum of the 'Area' column
            survived_sa <- sum(weekly_survived$Area)
            
        } else {
        # If the CSV file does not exist, fill in the total.sa value with NA
            survived_sa <- NA
        }
        
        # Add the week and total.sa values to the subject's data frame
        subject_data <- rbind(subject_data, data.frame(week = week_number,
                                                       survived.sa = survived_sa))
        
    }
    
    # Return the subject's data frame
    return(subject_data)
}
```
   
   Why is this coming up the same as segment.total_calc??
   
```{r}
subject_data <- data.frame()
# Input the correct file path
survived_folder <- "./Axon Classification/9022/W2_spotcomp"
ibranched_folder <- "./Axon Classification/9022/ibranched"
surfaces_folder <- "./Axon Classification/9022/Surfaces"
subject_data <- survived_calc(survived_folder, surfaces_folder)
subject_data
```  
   
   
    # Generate branch.sa column
    # Iterate over the 'ibranched' week numbers adding the data to the subject's data frame
    for (week_number in week_numbers) {
    # Check if the CSV file for the week exists in ibranched_folder
        csv_file <- paste0("W", week_number, ".csv")
        if (file.exists(file.path(ibranched_folder, csv_file))) {
            # If the CSV file exists, load it and area info
            weekly_ibranched <- read.csv(file.path(ibranched_folder, csv_file), skip = 3)
            weekly_surfaces <- read.csv(file.path(surfaces_folder, csv_file), skip = 3)
            # Merge ibranched and area info by ID number
            weekly_ibranched <- merge(weekly_ibranched, weekly_surfaces, by = "ID")
            
            # Load in survived data
            weekly_survived <- read.csv(file.path(survived_folder, csv_file), skip = 3)
            weekly_survived <- merge(weekly_survived, weekly_surfaces, by = "ID")
       
            # Calculate the sum of the 'Area' column
            ibranched_sa <- sum(weekly_ibranched$Area)
            survived_sa <- sum(weekly_survived$Area)
            ibranched_sa <- ibranched_sa - survived_sa
            
        } else {
        # If the CSV file does not exist, fill in the total.sa value with NA
            ibranched_sa <- NA
        }
        
        # Add the week and total.sa values to the subject's data frame
        subject_data$branch.sa <- ibranched_sa
    }
    
    # Generate new.sa column
    # Iterate over the 'surfaces' week numbers adding the data to the subject's data frame
    for (week_number in week_numbers) {
    # Check if the CSV file for the week exists in surfaces_folder
        csv_file <- paste0("W", week_number, ".csv")
        if (file.exists(file.path(surfaces_folder, csv_file))) {
            # If the CSV file exists, load it
            weekly_surfaces <- read.csv(file.path(surfaces_folder, csv_file), skip = 3)
            
            # Load in ibranched data and merge in area info
            weekly_ibranched <- read.csv(file.path(ibranched_folder, csv_file), skip = 3)
            weekly_ibranched <- merge(weekly_ibranched, weekly_surfaces, by = "ID")
          
            # Calculate the sum of the 'Area' column
            new_sa <- sum(weekly_surfaces$Area)
            new_sa <- new_sa - ibranched_sa
            
        } else {
        # If the CSV file does not exist, fill in the total.sa value with NA
            new_sa <- NA
        }
        
        # Add the week and total.sa values to the subject's data frame
        subject_data$new.sa <- new_sa
    }
    
    # Iterate over the week numbers and calculate the normalized surface area
    for (i in 1:14) {
        subject_data$norm.branch.sa <- subject_data$surfaces_sa / subject_data$segment.total.sa
        subject_data$norm.survived.sa <- subject_data$surfaces_sa / subject_data$segment.total.sa
        subject_data$norm.new.sa <- subject_data$surfaces_sa / subject_data$segment.total.sa
    }
    
    # Return the subject's data frame
    return(subject_data)
}

Lets test it out on 9022


```{r}
week_number <- "W-2.csv"
csv_file <- paste0("W", week_number, ".csv")
file.exists(file.path(ibranched_folder, csv_file))
```

