---
title: "Exploring GCaMP Exclusion Critereon"
author: "Patrick"
date: "2023-12-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goal: determine a criterion/metric by which to exclude responses that have an unstable baseline.

An unstable baseline can do a few things

1. May indicate a sponetous startle arrousal/respose that would prevent the animal from properly responding to the applied air puff.
2. May confound peak amplitude or rise times. Astrocytes display Ca2+ transients for reasons other than NE release and if they occur in the baseline

So how do we determine if the trial should be excluded?

1. Load in some example data for a variety of traces that I believe should be excluded - 5 of each?

2. Plot them on top of each other and look at the baseline to see what we can

Exclude:

- 9025.11
- 9025.12
- 9025.13
- 9203.11
- 9203.14
- 9025.72 (already loaded)
- 9023.11 (already loaded)

Packages
```{r}
library(Metrics)
library(data.table)
library(dplyr)
library(tidyverse)
library(gsignal)
library(npreg)
```

Load in and apply filter/vizualize data subset
```{r}
# Exclude 
file_path <- "./Functional_Noise_Proc/9025/W1/1.csv"
G9025.11 <- dff(file_path)
ss.9025.11 <- ss(G9025.11$time, G9025.11$dFF, nknots = 15, m = 2)
plot(G9025.11$time, G9025.11$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.11, G9025.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.11 <- predict(ss.9025.11, G9025.11$time)

file_path <- "./Functional_Noise_Proc/9025/W1/2.csv"
G9025.12 <- dff(file_path)
ss.9025.12 <- ss(G9025.12$time, G9025.12$dFF, nknots = 15, m = 2)
plot(G9025.12$time, G9025.12$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.12", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.12, G9025.12$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.12 <- predict(ss.9025.12, G9025.12$time)

file_path <- "./Functional_Noise_Proc/9025/W1/3.csv"
G9025.13 <- dff(file_path)
ss.9025.13 <- ss(G9025.13$time, G9025.13$dFF, nknots = 15, m = 2)
plot(G9025.13$time, G9025.13$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.13, G9025.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.13 <- predict(ss.9025.13, G9025.13$time)

file_path <- "./Functional_Noise_Proc/9203/W1/1.csv"
G9203.11 <- dff(file_path)
ss.9203.11 <- ss(G9203.11$time, G9203.11$dFF, nknots = 15, m = 2)
plot(G9203.11$time, G9203.11$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9203.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9203.11, G9203.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9203.11 <- predict(ss.9203.11, G9203.11$time)

file_path <- "./Functional_Noise_Proc/9203/W1/4.csv"
G9203.14 <- dff(file_path)
ss.9203.14 <- ss(G9203.14$time, G9203.14$dFF, nknots = 15, m = 2)
plot(G9203.14$time, G9203.14$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9203.14", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9203.14, G9203.14$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9203.14 <- predict(ss.9203.14, G9203.14$time)

ss.9025.72 <- ss(G9025.72$time, G9025.72$dFF, nknots = 15, m = 2)
plot(G9025.72$time, G9025.72$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.72", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.72, G9025.72$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.72 <- predict(ss.9025.72, G9025.72$time)

ss.9023.11 <- ss(G9023.11$time, G9023.11$dFF, nknots = 15, m = 2)
plot(G9023.11$time, G9023.11$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9023.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.11, G9023.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9023.11 <- predict(ss.9023.11, G9023.11$time)

#Include
ss.9023.12 <- ss(G9023.12$time, G9023.12$dFF, nknots = 15, m = 2)
plot(G9023.12$time, G9023.12$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9023.12", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.12, G9023.12$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9023.12 <- predict(ss.9023.12, G9023.12$time)

ss.9022.11 <- ss(G9022.11$time, G9022.11$dFF, nknots = 15, m = 2)
plot(G9022.11$time, G9022.11$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9022.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9022.11, G9022.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9022.11 <- predict(ss.9022.11, G9022.11$time)

ss.9022.13 <- ss(G9022.13$time, G9022.13$dFF, nknots = 15, m = 2)
plot(G9022.13$time, G9022.13$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9022.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9022.13, G9022.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9022.13 <- predict(ss.9022.13, G9022.13$time)

ss.9025.32 <- ss(G9025.32$time, G9025.32$dFF, nknots = 15, m = 2)
plot(G9025.32$time, G9025.32$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9025.32", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.32, G9025.32$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.32 <- predict(ss.9025.32, G9025.32$time)

ss.9025.53 <- ss(G9025.53$time, G9025.53$dFF, nknots = 15, m = 2)
plot(G9025.53$time, G9025.53$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9025.53", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.53, G9025.53$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.53 <- predict(ss.9025.53, G9025.53$time)

# Questionable
ss.9023.13 <- ss(G9023.13$time, G9023.13$dFF, nknots = 15, m = 2)
plot(G9023.13$time, G9023.13$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9023.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.13, G9023.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9023.13 <- predict(ss.9023.13, G9023.13$time)

ss.9023.33 <- ss(G9023.33$time, G9023.33$dFF, nknots = 15, m = 2)
plot(G9023.33$time, G9023.33$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9023.33", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.33, G9023.33$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9023.33 <- predict(ss.9023.33, G9023.33$time)

ss.9025.51 <- ss(G9025.51$time, G9025.51$dFF, nknots = 15, m = 2)
plot(G9025.51$time, G9025.51$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9025.51", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.51, G9025.51$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.51 <- predict(ss.9025.51, G9025.51$time)

ss.9203.53 <- ss(G9203.53$time, G9203.53$dFF, nknots = 15, m = 2)
plot(G9203.53$time, G9203.53$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9203.53", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9203.53, G9203.53$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9203.53 <- predict(ss.9203.53, G9203.53$time)
```

One big graph
```{r}
plot(G9202.32$time, G9202.32$dFF, type = "n", xlim = c(-8, 30), ylim = c(-0.5, 1.5), 
     main = "Exclusion Criteria Exploration", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.11, G9025.11$time), col = "deeppink", lwd = 2)
lines(predict(ss.9025.12, G9025.12$time), col = "deeppink", lwd = 2)
lines(predict(ss.9025.13, G9025.13$time), col = "deeppink", lwd = 2)
lines(predict(ss.9203.11, G9203.11$time), col = "deeppink", lwd = 2)
lines(predict(ss.9203.14, G9203.14$time), col = "deeppink", lwd = 2)
lines(predict(ss.9025.72, G9025.72$time), col = "deeppink", lwd = 2)
lines(predict(ss.9023.11, G9023.11$time), col = "deeppink", lwd = 2)
lines(predict(ss.9023.12, G9023.12$time), col = "chartreuse4", lwd = 2)
lines(predict(ss.9022.11, G9022.11$time), col = "chartreuse4", lwd = 2)
lines(predict(ss.9022.13, G9022.13$time), col = "chartreuse4", lwd = 2)
lines(predict(ss.9025.32, G9025.32$time), col = "chartreuse4", lwd = 2)
lines(predict(ss.9025.53, G9025.53$time), col = "chartreuse4", lwd = 2)
lines(predict(ss.9023.13, G9023.13$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9023.33, G9023.33$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9025.51, G9025.51$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9203.53, G9203.53$time), col = "darkgoldenrod", lwd = 2)
legend("topright", 
       legend = c("9025.11", "9025.12", "9025.13", "9203.11", "9203.14", "9025.72",
                  "9023.11", "9023.12", "9022.11", "9022.13", "9025.32", "9025.53",
                  "9023.13", "9023.33", "9025.51", "9203.53"),
       fill = c("deeppink", "deeppink", "deeppink", "deeppink", "deeppink",
                "deeppink", "deeppink", "chartreuse4", "chartreuse4", "chartreuse4",
                "chartreuse4", "chartreuse4", "darkgoldenrod", "darkgoldenrod",
                "darkgoldenrod", "darkgoldenrod"))
legend("topleft", legend = c("Exclude", "Include", "Questionable"), 
       fill = "deeppink", "chartreuse4", "darkgoldenrod")
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
```

Nothing immediately jumps out - lets find fit a linear model and find the variance to see if those align with my personal judgement. 

Calculate the slope of the filtered baseline by fitting a linear model

```{r}
lm9025.11 <- lm(y[11:50] ~ x[11:50], S9025.11)
lm9025.11
coef(lm9025.11)[2]

plot(G9025.11$time, G9025.11$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.11, G9025.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(lm9025.11, lwd = 2, col = "red")
```
Retrieve linear fit of the raw and filtered baseline
```{r}
## Exclude
lm9025.11 <- lm(dFF[11:50] ~ time[11:50], G9025.11)
s_lm9025.11 <- lm(y[11:50] ~ x[11:50], S9025.11)

lm9025.12 <- lm(dFF[11:50] ~ time[11:50], G9025.12)
s_lm9025.12 <- lm(y[11:50] ~ x[11:50], S9025.12)

lm9025.13 <- lm(dFF[11:50] ~ time[11:50], G9025.13)
s_lm9025.13 <- lm(y[11:50] ~ x[11:50], S9025.13)

lm9203.11 <- lm(dFF[11:50] ~ time[11:50], G9203.11)
s_lm9203.11 <- lm(y[11:50] ~ x[11:50], S9203.11)

lm9203.14 <- lm(dFF[11:50] ~ time[11:50], G9203.14)
s_lm9203.14 <- lm(y[11:50] ~ x[11:50], S9203.14)

lm9025.72 <- lm(dFF[11:50] ~ time[11:50], G9025.72)
s_lm9025.72 <- lm(y[11:50] ~ x[11:50], S9025.72)

lm9023.11 <- lm(dFF[11:50] ~ time[11:50], G9023.11)
s_lm9023.11 <- lm(y[11:50] ~ x[11:50], S9023.11)

## Include:
lm9023.12 <- lm(dFF[11:50] ~ time[11:50], G9023.12)
s_lm9023.12 <- lm(y[11:50] ~ x[11:50], S9023.12)

lm9022.11 <- lm(dFF[11:50] ~ time[11:50], G9022.11)
s_lm9022.11 <- lm(y[11:50] ~ x[11:50], S9022.11)

lm9022.13 <- lm(dFF[11:50] ~ time[11:50], G9022.13)
s_lm9022.13 <- lm(y[11:50] ~ x[11:50], S9022.13)

lm9025.32 <- lm(dFF[11:50] ~ time[11:50], G9025.32)
s_lm9025.32 <- lm(y[11:50] ~ x[11:50], S9025.32)

lm9025.53 <- lm(dFF[11:50] ~ time[11:50], G9025.53)
s_lm9025.53 <- lm(y[11:50] ~ x[11:50], S9025.53)

## Questionable:
lm9023.13 <- lm(dFF[11:50] ~ time[11:50], G9023.13)
s_lm9023.13 <- lm(y[11:50] ~ x[11:50], S9023.13)

lm9023.33 <- lm(dFF[11:50] ~ time[11:50], G9023.33)
s_lm9023.33 <- lm(y[11:50] ~ x[11:50], S9023.33)

lm9025.51 <- lm(dFF[11:50] ~ time[11:50], G9025.51)
s_lm9025.51 <- lm(y[11:50] ~ x[11:50], S9025.51)

lm9203.53 <- lm(dFF[11:50] ~ time[11:50], G9203.53)
s_lm9203.53 <- lm(y[11:50] ~ x[11:50], S9203.53)
```

Retrieve absolute value of the slope for each (want absolute value as we care about deviation from flat)
```{r}
## Exclude
slope9025.11 <- abs(coef(lm9025.11)[2])
s_slope9025.11 <- abs(coef(s_lm9025.11)[2])

slope9025.12 <- abs(coef(lm9025.12)[2])
s_slope9025.12 <- abs(coef(s_lm9025.12)[2])

slope9025.13 <- abs(coef(lm9025.13)[2])
s_slope9025.13 <- abs(coef(s_lm9025.13)[2])

slope9203.11 <- abs(coef(lm9203.11)[2])
s_slope9203.11 <- abs(coef(s_lm9203.11)[2])

slope9203.14 <- abs(coef(lm9203.14)[2])
s_slope9203.14 <- abs(coef(s_lm9203.14)[2])

slope9025.72 <- abs(coef(lm9025.72)[2])
s_slope9025.72 <- abs(coef(s_lm9025.72)[2])

slope9023.11 <- abs(coef(lm9023.11)[2])
s_slope9023.11 <- abs(coef(s_lm9023.11)[2])

## Include
slope9023.12 <- abs(coef(lm9023.12)[2])
s_slope9023.12 <- abs(coef(s_lm9023.12)[2])

slope9022.11 <- abs(coef(lm9022.11)[2])
s_slope9022.11 <- abs(coef(s_lm9022.11)[2])

slope9022.13 <- abs(coef(lm9022.13)[2])
s_slope9022.13 <- abs(coef(s_lm9022.13)[2])

slope9025.32 <- abs(coef(lm9025.32)[2])
s_slope9025.32 <- abs(coef(s_lm9025.32)[2])

slope9025.53 <- abs(coef(lm9025.53)[2])
s_slope9025.53 <- abs(coef(s_lm9025.53)[2])

## Questionable
slope9023.13 <- abs(coef(lm9023.13)[2])
s_slope9023.13 <- abs(coef(s_lm9023.13)[2])

slope9023.33 <- abs(coef(lm9023.33)[2])
s_slope9023.33 <- abs(coef(s_lm9023.33)[2])

slope9025.51 <- abs(coef(lm9025.51)[2])
s_slope9025.51 <- abs(coef(s_lm9025.51)[2])

slope9203.53 <- abs(coef(lm9203.53)[2])
s_slope9203.53 <- abs(coef(s_lm9203.53)[2])
```

Extract the variance of the filtered and raw baseline:
```{r}
var9025.11 <- var(S9025.11$y[11:50])
var9025.11
```

```{r}
## Exclude
var9025.11 <- var(G9025.11$dFF[11:50])
s_var9025.11 <- var(S9025.11$y[11:50])

var9025.12 <- var(G9025.12$dFF[11:50])
s_var9025.12 <- var(S9025.12$y[11:50])

var9025.13 <- var(G9025.13$dFF[11:50])
s_var9025.13 <- var(S9025.13$y[11:50])

var9203.11 <- var(G9203.11$dFF[11:50])
s_var9203.11 <- var(S9203.11$y[11:50])

var9203.14 <- var(G9203.14$dFF[11:50])
s_var9203.14 <- var(S9203.14$y[11:50])

var9025.72 <- var(G9025.72$dFF[11:50])
s_var9025.72 <- var(S9025.72$y[11:50])

var9023.11 <- var(G9023.11$dFF[11:50])
s_var9023.11 <- var(S9023.11$y[11:50])

## Include:
var9023.12 <- var(G9023.12$dFF[11:50])
s_var9023.12 <- var(S9023.12$y[11:50])

var9022.11 <- var(G9022.11$dFF[11:50])
s_var9022.11 <- var(S9022.11$y[11:50])

var9022.13 <- var(G9025.13$dFF[11:50])
s_var9022.13 <- var(S9025.13$y[11:50])

var9025.32 <- var(G9025.32$dFF[11:50])
s_var9025.32 <- var(S9025.32$y[11:50])

var9025.53 <- var(G9025.53$dFF[11:50])
s_var9025.53 <- var(S9025.53$y[11:50])

## Questionable:
var9023.13 <- var(G9023.13$dFF[11:50])
s_var9023.13 <- var(S9023.13$y[11:50])

var9023.33 <- var(G9023.33$dFF[11:50])
s_var9023.33 <- var(S9023.33$y[11:50])

var9025.51 <- var(G9025.51$dFF[11:50])
s_var9025.51 <- var(S9025.51$y[11:50])

var9203.53 <- var(G9203.53$dFF[11:50])
s_var9203.53 <- var(S9203.53$y[11:50]) 
```


Make a table:
```{r}
inclusion_exp <- data.frame()
inclusion_exp[1:16, ] <- NA
inclusion_exp$id <- c(9025.11, 9025.12, 9025.13, 9203.11, 9203.14, 9025.72, 9023.11,
                      9023.12, 9022.11, 9022.13, 9025.32, 9025.53, 9023.13, 9023.33,
                      9025.51, 9203.53)
inclusion_exp$Rtype <- c("Exclude", "Exclude", "Exclude", "Exclude", "Exclude", "Exclude",
                       "Exclude", "Include", "Include", "Include", "Include", "Include",
                       "Questionable", "Questionable", "Questionable", "Questionable")
inclusion_exp$rawslope <- c(slope9025.11, slope9025.12, slope9025.13, slope9203.11,
                            slope9203.14, slope9025.72, slope9023.11, slope9023.12,
                            slope9022.11, slope9022.13, slope9025.32, slope9025.53,
                            slope9023.13, slope9023.33, slope9025.51, slope9203.53)
inclusion_exp$filtslope <- c(s_slope9025.11, s_slope9025.12, s_slope9025.13, s_slope9203.11,
                             s_slope9203.14, s_slope9025.72, s_slope9023.11, s_slope9023.12,
                             s_slope9022.11, s_slope9022.13, s_slope9025.32, s_slope9025.53,
                             s_slope9023.13, s_slope9023.33, s_slope9025.51, s_slope9203.53)
inclusion_exp$rawvar <- c(var9025.11, var9025.12, var9025.13, var9203.11,
                          var9203.14, var9025.72, var9023.11, var9023.12,
                          var9022.11, var9022.13, var9025.32, var9025.53,
                          var9023.13, var9023.33, var9025.51, var9203.53)
inclusion_exp$filtvar <- c(s_var9025.11, s_var9025.12, s_var9025.13, s_var9203.11,
                           s_var9203.14, s_var9025.72, s_var9023.11, s_var9023.12,
                           s_var9022.11, s_var9022.13, s_var9025.32, s_var9025.53,
                           s_var9023.13, s_var9023.33, s_var9025.51, s_var9203.53)
inclusion_exp
write.csv(inclusion_exp, file = "./GCaMP_insclusion_criteria.csv", row.names = FALSE)
```
Lets remake the graphs with a slope on each

```{r}
# Exclude 
plot(G9025.11$time, G9025.11$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.11, G9025.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9025.11, lwd = 1, col = "green")
abline(lm9025.11, lwd = 1, col = "black")

plot(G9025.12$time, G9025.12$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.12", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.12, G9025.12$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9025.12, lwd = 1, col = "green")
abline(lm9025.12, lwd = 1, col = "black")

plot(G9025.13$time, G9025.13$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.13, G9025.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9025.13, lwd = 1, col = "green")
abline(lm9025.13, lwd = 1, col = "black")

plot(G9203.11$time, G9203.11$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9203.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9203.11, G9203.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9203.11, lwd = 1, col = "green")
abline(lm9203.11, lwd = 1, col = "black")

plot(G9203.14$time, G9203.14$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9203.14", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9203.14, G9203.14$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9203.14, lwd = 1, col = "green")
abline(lm9203.14, lwd = 1, col = "black")

plot(G9025.72$time, G9025.72$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.72", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.72, G9025.72$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9025.72, lwd = 1, col = "green")
abline(lm9025.72, lwd = 1, col = "black")

plot(G9023.11$time, G9023.11$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9023.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.11, G9023.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9023.11, lwd = 1, col = "green")
abline(lm9023.11, lwd = 1, col = "black")

#Include
plot(G9023.12$time, G9023.12$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9023.12", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.12, G9023.12$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9023.12, lwd = 1, col = "green")
abline(lm9023.12, lwd = 1, col = "black")

plot(G9022.11$time, G9022.11$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9022.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9022.11, G9022.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9022.11, lwd = 1, col = "green")
abline(lm9022.11, lwd = 1, col = "black")

plot(G9022.13$time, G9022.13$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9022.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9022.13, G9022.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9022.13, lwd = 1, col = "green")
abline(lm9022.13, lwd = 1, col = "black")

plot(G9025.32$time, G9025.32$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9025.32", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.32, G9025.32$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9025.32, lwd = 1, col = "green")
abline(lm9025.32, lwd = 1, col = "black")

plot(G9025.53$time, G9025.53$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9025.53", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.53, G9025.53$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9025.53, lwd = 1, col = "green")
abline(lm9025.53, lwd = 1, col = "black")

# Questionable
plot(G9023.13$time, G9023.13$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9023.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.13, G9023.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9023.13, lwd = 1, col = "green")
abline(lm9023.13, lwd = 1, col = "black")

plot(G9023.33$time, G9023.33$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9023.33", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.33, G9023.33$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9023.33, lwd = 1, col = "green")
abline(lm9023.33, lwd = 1, col = "black")

plot(G9025.51$time, G9025.51$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9025.51", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.51, G9025.51$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9025.11, lwd = 1, col = "green")
abline(lm9025.11, lwd = 1, col = "black")

plot(G9203.53$time, G9203.53$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9203.53", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9203.53, G9203.53$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
abline(s_lm9203.53, lwd = 1, col = "green")
abline(lm9203.53, lwd = 1, col = "black")
```

After discussing it with David, we would like to look at the range of the baseline as a criteria with a potential threshold of 0.5 - Lets grab the baseline ranges from all of these traces and line them up. We'll then remake the graphs labeling them according to that threshold and see where they sit.

Calculate the ranges
```{r}
range9025.11 <- max(S9025.11$y[11:50]) - min(S9025.11$y[11:50])
range9025.11
```


```{r}
range9025.11 <- max(S9025.11$y[11:50]) - min(S9025.11$y[11:50])
range9025.12 <- max(S9025.12$y[11:50]) - min(S9025.12$y[11:50])
range9025.13 <- max(S9025.13$y[11:50]) - min(S9025.13$y[11:50])
range9203.11 <- max(S9203.11$y[11:50]) - min(S9203.11$y[11:50])
range9203.14 <- max(S9203.14$y[11:50]) - min(S9203.14$y[11:50])
range9025.72 <- max(S9025.72$y[11:50]) - min(S9025.72$y[11:50])
range9023.11 <- max(S9023.11$y[11:50]) - min(S9023.11$y[11:50])
range9023.12 <- max(S9023.12$y[11:50]) - min(S9023.12$y[11:50])
range9022.11 <- max(S9022.11$y[11:50]) - min(S9022.11$y[11:50])
range9022.13 <- max(S9022.13$y[11:50]) - min(S9022.13$y[11:50])
range9025.32 <- max(S9025.32$y[11:50]) - min(S9025.32$y[11:50])
range9025.53 <- max(S9025.53$y[11:50]) - min(S9025.53$y[11:50])
range9023.13 <- max(S9023.13$y[11:50]) - min(S9023.13$y[11:50])
range9023.33 <- max(S9023.33$y[11:50]) - min(S9023.33$y[11:50])
range9025.51 <- max(S9025.51$y[11:50]) - min(S9025.51$y[11:50])
range9203.53 <- max(S9203.53$y[11:50]) - min(S9203.53$y[11:50])
```

Add them to the table
```{r}
inclusion_exp$filtrange <- c(range9025.11, range9025.12, range9025.13, range9203.11,
                             range9203.14, range9025.72, range9023.11, range9023.12,
                             range9022.11, range9022.13, range9025.32, range9025.53,
                             range9023.13, range9023.33, range9025.51, range9203.53)
inclusion_exp
write.csv(inclusion_exp, file = "./GCaMP_insclusion_criteria.csv", row.names = FALSE)
```
New plots with titles according to the exclusion threshold

```{r}
# Include
plot(G9025.11$time, G9025.11$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9025.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.11, G9025.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9025.12$time, G9025.12$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9025.12", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.12, G9025.12$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9203.11$time, G9203.11$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9203.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9203.11, G9203.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9023.11$time, G9023.11$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9023.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.11, G9023.11$time[11:200]), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9023.12$time, G9023.12$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9023.12", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.12, G9023.12$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9022.11$time, G9022.11$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9022.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9022.11, G9022.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9022.13$time, G9022.13$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9022.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9022.13, G9022.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9025.32$time, G9025.32$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9025.32", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.32, G9025.32$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9025.53$time, G9025.53$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9025.53", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.53, G9025.53$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9023.13$time, G9023.13$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9023.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.13, G9023.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9023.33$time, G9023.33$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9023.33", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.33, G9023.33$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9203.53$time, G9203.53$dFF, type = "l", xlim = c(-8, 30), main = "Include: G9203.53", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9203.53, G9203.53$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

# Exclude
plot(G9025.51$time, G9025.51$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.51", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.51, G9025.51$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9025.72$time, G9025.72$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.72", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.72, G9025.72$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9203.14$time, G9203.14$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9203.14", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9203.14, G9203.14$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)

plot(G9025.13$time, G9025.13$dFF, type = "l", xlim = c(-8, 30), main = "Exclude: G9025.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.13, G9025.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
```
```{r}
G9023.11
```

