---
title: "Exploring GCaMP Success Metrics"
author: "Patrick"
date: "2023-12-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goal: determine a metric to assign a GCaMP response as a successful or failed response.

Two methods: to try:

1) Root mean squared deviation/error: quadratic mean of the differences between the observed values and predicted ones. Aggregates the magnitudes of the errors in predictions for various data points into a single measure of predictive power.

- RMSE basically measures how far off an actual value is from the model's prediction for that value. 
- Uses rmse() function from the Metrics package

2) Z-Score:statistical measurement that describes a value's relationship to the mean of a group of values. Basically the number of standard deviations that the signal differs from the initial signal.
- z score = (peak amplitude of response - mean of the population) / standard deviation of the population

Do we use the raw data or smoothed data?

Packages
```{r}
library(Metrics)
library(data.table)
library(dplyr)
library(tidyverse)
library(gsignal)
library(npreg)
```
Objects for the smoothed data
```{r}
# No Response
S9202.32 <- predict(ss.1, G9202.32$time)
S9203.53 <- predict(ss.2, G9203.53$time)
# Good Response
S9202.31 <- predict(ss.3, G9202.31$time)
S9204.13 <- predict(ss.4, G9204.13$time)
# Poor Response
S9204.11 <- predict(ss.5, G9204.11$time)
S9202.12 <- predict(ss.6, G9202.12$time)
# Questionable Response
S9202.13 <- predict(ss.7, G9202.13$time)
S9203.31 <- predict(ss.8, G9203.31$time)
# Early Response
S9202.33 <- predict(ss.9, G9202.33$time)
S9203.51 <- predict(ss.10, G9203.51$time)
```

## Looking at RMSE

Calculate the rmse values for the raw and filtered values
```{r}
# No Response
rmse9202.32 <- rmse(G9202.32$dFF[51:200], G9202.32$dFF[11:50])
s_rmse9202.32 <- rmse(S9202.32$y[51:200], S9202.32$y[11:50])

rmse9203.53 <- rmse(G9203.53$dFF[51:200], G9203.53$dFF[11:50])
s_rmse9203.53 <- rmse(S9203.53$y[51:200], S9203.53$y[11:50])
# Good Response
rmse9202.31 <- rmse(G9202.31$dFF[51:200], G9202.31$dFF[11:50])
s_rmse9202.31 <- rmse(S9202.31$y[51:200], S9202.31$y[11:50])

rmse9204.13 <- rmse(G9204.13$dFF[51:200], G9204.13$dFF[11:50])
s_rmse9204.13 <- rmse(S9204.13$y[51:200], S9204.13$y[11:50])
# Poor Response
rmse9204.11 <- rmse(G9204.11$dFF[51:200], G9204.11$dFF[11:50])
s_rmse9204.11 <- rmse(S9204.11$y[51:200], S9204.11$y[11:50])

rmse9202.12 <- rmse(G9202.12$dFF[51:200], G9202.12$dFF[11:50])
s_rmse9202.12 <- rmse(S9202.12$y[51:200], S9202.12$y[11:50])
# Questionable
rmse9202.13 <- rmse(G9202.13$dFF[51:200], G9202.13$dFF[11:50])
s_rmse9202.13 <- rmse(S9202.13$y[51:200], S9202.13$y[11:50])

rmse9203.31 <- rmse(G9203.31$dFF[51:200], G9203.31$dFF[11:50])
s_rmse9203.31 <- rmse(S9203.31$y[51:200], S9203.31$y[11:50])
# Early Response
rmse9202.33 <- rmse(G9202.33$dFF[51:200], G9202.33$dFF[11:50])
s_rmse9202.33 <- rmse(S9202.33$y[51:200], S9202.33$y[11:50])

rmse9203.51 <- rmse(G9203.51$dFF[51:200], G9203.51$dFF[11:50])
s_rmse9203.51 <- rmse(S9203.51$y[51:200], S9203.51$y[11:50])
```

Build a data frame for the rmse results comparing smooth data to raw data scores
```{r}
success_exp <- data.frame()
success_exp[1:10, ] <- NA
success_exp$id <- c(9202.32, 9203.53, 9202.31, 9204.13, 9204.11, 9202.12, 9202.13,
                 9203.31, 9202.33, 9203.51)
success_exp$Rtype <- c("No", "No", "Good", "Good", "Poor", "Poor", "Questionable",
                       "Questionable", "Early", "Early")
success_exp$rawrmse <- c(rmse9202.32, rmse9203.53, rmse9202.31, rmse9204.13, rmse9204.11,
                       rmse9202.12, rmse9202.13, rmse9203.31, rmse9202.33, rmse9203.51)
success_exp$smoothrmse <- c(s_rmse9202.32, s_rmse9203.53, s_rmse9202.31, s_rmse9204.13,
                          s_rmse9204.11, s_rmse9202.12, s_rmse9202.13, s_rmse9203.31,
                          s_rmse9202.33, s_rmse9203.51)
success_exp
```

Impression: rawvrmse are always greater than smoothrmse. Values follow the assignments. Is it a response? values allign with no response

# Adding Z Scores
Peak amplitude of response is max value from 51:200
standard deviation of population will be sd(11:50)

Looking at Z Scores for No Response 9202.32
```{r}
max(G9202.32$dFF[51:200]) / sd(G9202.32$dFF[11:50])
max(S9202.32$y[51:200]) / sd(S9202.32$y[11:50])
max(G9202.32$dFF[51:200])
sd(G9202.32$dFF[11:50])
max(S9202.32$y[51:200])
sd(S9202.32$y[11:50])
```
OK whats the zscore of the baseline?

```{r}
# NR 9202.32
max(G9202.32$dFF[11:50]) / sd(G9202.32$dFF[11:50])
max(S9202.32$y[11:50]) / sd(S9202.32$y[11:50])

# NR 9203.53
max(G9203.53$dFF[11:50]) / sd(G9203.53$dFF[11:50])
max(S9203.53$y[11:50]) / sd(S9203.53$y[11:50])
```


```{r}
# No Response
z9202.32 <- max(G9202.32$dFF[51:200]) / sd(G9202.32$dFF[11:50])
s_z9202.32 <- max(S9202.32$y[51:200]) / sd(S9202.32$y[11:50])

z9203.53 <- max(G9203.53$dFF[51:200]) / sd(G9203.53$dFF[11:50])
s_z9203.53 <- max(S9203.53$y[51:200]) / sd(S9203.53$y[11:50])
# Good Response
z9202.31 <- max(G9202.31$dFF[51:200]) / sd(G9202.31$dFF[11:50])
s_z9202.31 <- max(S9202.31$y[51:200]) / sd(S9202.31$y[11:50])

z9204.13 <- max(G9204.13$dFF[51:200]) / sd(G9204.13$dFF[11:50])
s_z9204.13 <- max(S9204.13$y[51:200]) / sd(S9204.13$y[11:50])
# Poor Response
z9204.11 <- max(G9204.11$dFF[51:200]) / sd(G9204.11$dFF[11:50])
s_z9204.11 <- max(S9204.11$y[51:200]) / sd(S9204.11$y[11:50])

z9202.12 <- max(G9202.12$dFF[51:200]) / sd(G9202.12$dFF[11:50])
s_z9202.12 <- max(S9202.12$y[51:200]) / sd(S9202.12$y[11:50])
# Is it a response?
z9202.13 <- max(G9202.13$dFF[51:200]) / sd(G9202.13$dFF[11:50])
s_z9202.13 <- max(S9202.13$y[51:200]) / sd(S9202.13$y[11:50])

z9203.31 <- max(G9203.31$dFF[51:200]) / sd(G9203.31$dFF[11:50])
s_z9203.31 <- max(S9203.31$y[51:200]) / sd(S9203.31$y[11:50])
# Early Response
z9202.33 <- max(G9202.33$dFF[51:200]) / sd(G9202.33$dFF[11:50])
s_z9202.33 <- max(S9202.33$y[51:200]) / sd(S9202.33$y[11:50])

z9203.51 <- max(G9203.51$dFF[51:200]) / sd(G9203.51$dFF[11:50])
s_z9203.51 <- max(S9203.51$y[51:200]) / sd(S9203.51$y[11:50])
```

Add the values into the table

```{r}
success_exp$rawz <- c(z9202.32, z9203.53, z9202.31, z9204.13, z9204.11,
                       z9202.12, z9202.13, z9203.31, z9202.33, z9203.51)
success_exp$smoothz <- c(s_z9202.32, s_z9203.53, s_z9202.31, s_z9204.13,
                          s_z9204.11, s_z9202.12, s_z9202.13, s_z9203.31,
                          s_z9202.33, s_z9203.51)
success_exp <- success_exp[order(success_exp$rawz),]
success_exp
```
Looks like both methods show promise.

# Determining final criteria
Lets add some more non-responses and responses to the mix that extends the spectrum and see how it works.

Loading in additional responses
No Response:
9023 W1 P2
9022 W1 P1
9022 W1 P3
9025 W5 P3

Early
9023 W1 P1
9025 W7 P2

Questionable
9025 W3 P2

Response
9025 W1 P4 - poor/alright
9023 W1 P3 - poor
9023 W3 P3 - alright
9022 W5 P1 - good
9025 W5 P1 - alright/good
9023 W5 P2 - poor/alright
9025 W7 P3 - good
9025 W7 P4 - alright

```{r}
## No Response
file_path <- "./Functional_Noise_Proc/9023/W1/2.csv"
G9023.12 <- dff(file_path)
with(G9023.12, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9022/W1/1.csv"
G9022.11 <- dff(file_path)
with(G9022.11, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9022/W1/3.csv"
G9022.13 <- dff(file_path)
with(G9022.13, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9025/W5/3.csv"
G9025.53 <- dff(file_path)
with(G9025.53, plot(time, dFF, type = "l"))

## Early Response
file_path <- "./Functional_Noise_Proc/9023/W1/1.csv"
G9023.11 <- dff(file_path)
with(G9023.11, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9025/W7/2.csv"
G9025.72 <- dff(file_path)
with(G9025.72, plot(time, dFF, type = "l"))

## Questionable Response
file_path <- "./Functional_Noise_Proc/9025/W3/2.csv"
G9025.32 <- dff(file_path)
with(G9025.32, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9023/W3/3.csv"
G9023.33 <- dff(file_path)
with(G9023.33, plot(time, dFF, type = "l"))

## Responses
file_path <- "./Functional_Noise_Proc/9025/W1/4.csv"
G9025.14 <- dff(file_path)
with(G9025.14, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9023/W1/3.csv"
G9023.13 <- dff(file_path)
with(G9023.13, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9022/W5/1.csv"
G9022.51 <- dff(file_path)
with(G9022.51, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9025/W5/1.csv"
G9025.51 <- dff(file_path)
with(G9025.51, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9023/W5/2.csv"
G9023.52 <- dff(file_path)
with(G9023.52, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9025/W7/3.csv"
G9025.73 <- dff(file_path)
with(G9025.73, plot(time, dFF, type = "l"))

file_path <- "./Functional_Noise_Proc/9025/W7/4.csv"
G9025.74 <- dff(file_path)
with(G9025.74, plot(time, dFF, type = "l"))
```
Get the smoothing lines

```{r}
## No Response
ss.9023.12 <- ss(G9023.12$time, G9023.12$dFF, nknots = 15, m = 2)
plot(G9023.12$time, G9023.12$dFF, type = "l", xlim = c(-8, 30), main = "No Response: G9023.12", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.12, G9023.12$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9023.12 <- predict(ss.9023.12, G9023.12$time)

ss.9022.11 <- ss(G9022.11$time, G9022.11$dFF, nknots = 15, m = 2)
plot(G9022.11$time, G9022.11$dFF, type = "l", xlim = c(-8, 30), main = "No Response: G9022.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9022.11, G9022.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9022.11 <- predict(ss.9022.11, G9022.11$time)

ss <- ss(G9022.13$time, G9022.13$dFF, nknots = 15, m = 2)
plot(G9022.13$time, G9022.13$dFF, type = "l", xlim = c(-8, 30), main = "No Response: G9022.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss, G9022.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9022.13 <- predict(ss, G9022.13$time)

## Early Response
ss <- ss(G9023.11$time, G9023.11$dFF, nknots = 15, m = 2)
plot(G9023.11$time, G9023.11$dFF, type = "l", xlim = c(-8, 30), main = "Early Response: G9023.11", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss, G9023.11$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9023.11 <- predict(ss, G9023.11$time)

ss <- ss(G9025.72$time, G9025.72$dFF, nknots = 15, m = 2)
plot(G9025.72$time, G9025.72$dFF, type = "l", xlim = c(-8, 30), main = "Early Response: G9025.72", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss, G9025.72$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.72 <- predict(ss, G9025.72$time)

## Questionable Response
ss <- ss(G9025.32$time, G9025.32$dFF, nknots = 15, m = 2)
plot(G9025.32$time, G9025.32$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9025.32", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss, G9025.32$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.32 <- predict(ss, G9025.32$time)

ss <- ss(G9023.33$time, G9023.33$dFF, nknots = 15, m = 2)
plot(G9023.33$time, G9023.33$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9023.33", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss, G9023.33$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9023.33 <- predict(ss, G9023.33$time)

ss.9023.13 <- ss(G9023.13$time, G9023.13$dFF, nknots = 15, m = 2)
plot(G9023.13$time, G9023.13$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9023.13", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9023.13, G9023.13$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9023.13 <- predict(ss.9023.13, G9023.13$time)

ss.9025.53 <- ss(G9025.53$time, G9025.53$dFF, nknots = 15, m = 2)
plot(G9025.53$time, G9025.53$dFF, type = "l", xlim = c(-8, 30), main = "Questionable: G9025.53", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.53, G9025.53$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.53 <- predict(ss.9025.53, G9025.53$time)

## Responses
ss.9025.14 <- ss(G9025.14$time, G9025.14$dFF, nknots = 15, m = 2)
plot(G9025.14$time, G9025.14$dFF, type = "l", xlim = c(-8, 30), main = "Yes Response: G9025.14", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.14, G9025.14$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.14 <- predict(ss.9025.14, G9025.14$time)

ss <- ss(G9022.51$time, G9022.51$dFF, nknots = 15, m = 2)
plot(G9022.51$time, G9022.51$dFF, type = "l", xlim = c(-8, 30), main = "Yes Response: G9022.51", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss, G9022.51$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9022.51 <- predict(ss, G9022.51$time)

ss.9025.51 <- ss(G9025.51$time, G9025.51$dFF, nknots = 15, m = 2)
plot(G9025.51$time, G9025.51$dFF, type = "l", xlim = c(-8, 30), main = "Yes Response: G9025.51", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.51, G9025.51$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.51 <- predict(ss.9025.51, G9025.51$time)

ss <- ss(G9023.52$time, G9023.52$dFF, nknots = 15, m = 2)
plot(G9023.52$time, G9023.52$dFF, type = "l", xlim = c(-8, 30), main = "Yes Response: G9023.52", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss, G9023.52$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9023.52 <- predict(ss, G9023.52$time)

ss.9025.73 <- ss(G9025.73$time, G9025.73$dFF, nknots = 15, m = 2)
plot(G9025.73$time, G9025.73$dFF, type = "l", xlim = c(-8, 30), main = "Yes Response: G9025.73", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.73, G9025.73$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.73 <- predict(ss.9025.73, G9025.73$time)

ss.9025.74 <- ss(G9025.74$time, G9025.74$dFF, nknots = 15, m = 2)
plot(G9025.74$time, G9025.74$dFF, type = "l", xlim = c(-8, 30), main = "Yes Response: G9025.74", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.74, G9025.74$time), col = "green", lwd = 2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
S9025.74 <- predict(ss.9025.74, G9025.74$time)
```

Calculate rmse for the raw and filtered values

```{r}
## No Response
rmse9023.12 <- rmse(G9023.12$dFF[51:200], G9023.12$dFF[11:50])
s_rmse9023.12 <- rmse(S9023.12$y[51:200], S9023.12$y[11:50])

rmse9022.11 <- rmse(G9022.11$dFF[51:200], G9022.11 $dFF[11:50])
s_rmse9022.11 <- rmse(S9022.11$y[51:200], S9022.11$y[11:50])

rmse9022.13 <- rmse(G9022.13$dFF[51:200], G9022.13 $dFF[11:50])
s_rmse9022.13 <- rmse(S9022.13$y[51:200], S9022.13$y[11:50])

rmse9025.53 <- rmse(G9025.53$dFF[51:200], G9025.53 $dFF[11:50])
s_rmse9025.53 <- rmse(S9025.53$y[51:200], S9025.53$y[11:50])

## Early Response
rmse9023.11 <- rmse(G9023.11$dFF[51:200], G9023.11 $dFF[11:50])
s_rmse9023.11 <- rmse(S9023.11$y[51:200], S9023.11$y[11:50])

rmse9025.72 <- rmse(G9025.72$dFF[51:200], G9025.72 $dFF[11:50])
s_rmse9025.72 <- rmse(S9025.72$y[51:200], S9025.72$y[11:50])

## Questionable Response
rmse9025.32<- rmse(G9025.32$dFF[51:200], G9025.32 $dFF[11:50])
s_rmse9025.32 <- rmse(S9025.32$y[51:200], S9025.32$y[11:50])

rmse9023.33 <- rmse(G9023.33$dFF[51:200], G9023.33 $dFF[11:50])
s_rmse9023.33 <- rmse(S9023.33$y[51:200], S9023.33$y[11:50])

## Response
rmse9025.14<- rmse(G9025.14$dFF[51:200], G9025.14 $dFF[11:50])
s_rmse9025.14 <- rmse(S9025.14$y[51:200], S9025.14$y[11:50])

rmse9023.13 <- rmse(G9023.13$dFF[51:200], G9023.13 $dFF[11:50])
s_rmse9023.13 <- rmse(S9023.13$y[51:200], S9023.13$y[11:50])

rmse9022.51 <- rmse(G9022.51$dFF[51:200], G9022.51 $dFF[11:50])
s_rmse9022.51 <- rmse(S9022.51$y[51:200], S9022.51$y[11:50])

rmse9025.51 <- rmse(G9025.51$dFF[51:200], G9025.51 $dFF[11:50])
s_rmse9025.51 <- rmse(S9025.51$y[51:200], S9025.51$y[11:50])

rmse9023.52 <- rmse(G9023.52$dFF[51:200], G9023.52 $dFF[11:50])
s_rmse9023.52 <- rmse(S9023.52$y[51:200], S9023.52$y[11:50])

rmse9025.73<- rmse(G9025.73$dFF[51:200], G9025.73 $dFF[11:50])
s_rmse9025.73 <- rmse(S9025.73$y[51:200], S9025.73$y[11:50])

rmse9025.74 <- rmse(G9025.74$dFF[51:200], G9025.74 $dFF[11:50])
s_rmse9025.74 <- rmse(S9025.74$y[51:200], S9025.74$y[11:50])
```

Calculate Z-scores for raw and smoothed values

```{r}
# No Response
z9023.12 <- max(G9023.12$dFF[51:200]) / sd(G9023.12$dFF[11:50])
s_z9023.12 <- max(S9023.12$y[51:200]) / sd(S9023.12$y[11:50])

z9022.11 <- max(G9022.11$dFF[51:200]) / sd(G9022.11$dFF[11:50])
s_z9022.11 <- max(S9022.11$y[51:200]) / sd(S9022.11$y[11:50])

z9022.13 <- max(G9022.13$dFF[51:200]) / sd(G9022.13$dFF[11:50])
s_z9022.13 <- max(S9022.13$y[51:200]) / sd(S9022.13$y[11:50])

z9025.53 <- max(G9025.53$dFF[51:200]) / sd(G9025.53$dFF[11:50])
s_z9025.53 <- max(S9025.53$y[51:200]) / sd(S9025.53$y[11:50])

# Early Response
z9023.11 <- max(G9023.11$dFF[51:200]) / sd(G9023.11$dFF[11:50])
s_z9023.11 <- max(S9023.11$y[51:200]) / sd(S9023.11$y[11:50])

z9025.72 <- max(G9025.72$dFF[51:200]) / sd(G9025.72$dFF[11:50])
s_z9025.72 <- max(S9025.72$y[51:200]) / sd(S9025.72$y[11:50])

## Questionable Response
z9025.32 <- max(G9025.32$dFF[51:200]) / sd(G9025.32$dFF[11:50])
s_z9025.32 <- max(S9025.32$y[51:200]) / sd(S9025.32$y[11:50])

z9023.33 <- max(G9023.33$dFF[51:200]) / sd(G9023.33$dFF[11:50])
s_z9023.33 <- max(S9023.33$y[51:200]) / sd(S9023.33$y[11:50])

# Responses
z9025.14 <- max(G9025.14$dFF[51:200]) / sd(G9025.14$dFF[11:50])
s_z9025.14 <- max(S9025.14$y[51:200]) / sd(S9025.14$y[11:50])

z9023.13 <- max(G9023.13$dFF[51:200]) / sd(G9023.13$dFF[11:50])
s_z9023.13 <- max(S9023.13$y[51:200]) / sd(S9023.13$y[11:50])

z9022.51 <- max(G9022.51$dFF[51:200]) / sd(G9022.51$dFF[11:50])
s_z9022.51 <- max(S9022.51$y[51:200]) / sd(S9022.51$y[11:50])

z9025.51 <- max(G9025.51$dFF[51:200]) / sd(G9025.51$dFF[11:50])
s_z9025.51 <- max(S9025.51$y[51:200]) / sd(S9025.51$y[11:50])

z9023.52 <- max(G9023.52$dFF[51:200]) / sd(G9023.52$dFF[11:50])
s_z9023.52 <- max(S9023.52$y[51:200]) / sd(S9023.52$y[11:50])

z9025.73 <- max(G9025.73$dFF[51:200]) / sd(G9025.73$dFF[11:50])
s_z9025.73 <- max(S9025.73$y[51:200]) / sd(S9025.73$y[11:50])

z9025.74 <- max(G9025.74$dFF[51:200]) / sd(G9025.74$dFF[11:50])
s_z9025.74 <- max(S9025.74$y[51:200]) / sd(S9025.74$y[11:50])
```

Next compile the new scores into the table and save the table as a CSV. Then save each new image with the green line.

```{r}
success_exp <- data.frame()
success_exp[1:25, ] <- NA
success_exp$id <- c(9202.32, 9203.53, 9202.31, 9204.13, 9204.11, 9202.12, 9202.13,
                 9203.31, 9202.33, 9203.51, 9023.12, 9022.11, 9022.13, 9025.53, 
                 9023.11, 9025.72, 9025.32, 9023.33, 9025.14, 9023.13, 9022.51, 
                 9025.51, 9023.52, 9025.73, 9025.74)
success_exp$Rtype <- c("No", "No", "Yes", "Yes", "Questionable", "Questionable", "Questionable",
                       "Questionable", "Early", "Yes", "No", "No", "No", "Questionable",
                       "Early", "Early", "Questionable", "Questionable", "Yes", 
                       "Questionable", "Yes", "Yes", "Yes", "Yes", "Yes")
success_exp$rawrmse <- c(rmse9202.32, rmse9203.53, rmse9202.31, rmse9204.13, rmse9204.11,
                       rmse9202.12, rmse9202.13, rmse9203.31, rmse9202.33, rmse9203.51,
                       rmse9023.12, rmse9022.11, rmse9022.13, rmse9025.53, rmse9023.11,
                       rmse9025.72, rmse9025.32, rmse9023.33, rmse9025.14, rmse9023.13,
                       rmse9022.51, rmse9025.51, rmse9023.52, rmse9025.73, rmse9025.74)
success_exp$smoothrmse <- c(s_rmse9202.32, s_rmse9203.53, s_rmse9202.31, s_rmse9204.13,
                          s_rmse9204.11, s_rmse9202.12, s_rmse9202.13, s_rmse9203.31,
                          s_rmse9202.33, s_rmse9203.51, s_rmse9023.12, s_rmse9022.11, 
                          s_rmse9022.13, s_rmse9025.53, s_rmse9023.11, s_rmse9025.72, 
                          s_rmse9025.32, s_rmse9023.33, s_rmse9025.14, s_rmse9023.13, 
                          s_rmse9022.51, s_rmse9025.51, s_rmse9023.52, s_rmse9025.73,
                          s_rmse9025.74)
success_exp$rawz <- c(z9202.32, z9203.53, z9202.31, z9204.13, z9204.11, z9202.12,
                      z9202.13, z9203.31, z9202.33, z9203.51, z9023.12,
                      z9022.11, z9022.13, z9025.53, z9023.11, z9025.72, z9025.32,
                      z9023.33, z9025.14, z9023.13, z9022.51, z9025.51, z9023.52,
                      z9025.73, z9025.74)
success_exp$smoothz <- c(s_z9202.32, s_z9203.53, s_z9202.31, s_z9204.13, s_z9204.11,
                         s_z9202.12, s_z9202.13, s_z9203.31, s_z9202.33, s_z9203.51,
                         s_z9023.12, s_z9022.11, s_z9022.13, s_z9025.53, s_z9023.11,
                         s_z9025.72, s_z9025.32, s_z9023.33, s_z9025.14, s_z9023.13,
                         s_z9022.51,s_z9025.51, s_z9023.52, s_z9025.73, s_z9025.74)
success_exp
write.csv(success_exp, file = "./GCaMP_succ_criteria.csv", row.names = FALSE)
```

rmse and z score provide similar results - I think using z-score on the raw data makes the most sense based on how the data looks and because the calculation is more straightforward than rmse

Where to put the success threshold?

## Looking at fringe cases

Fringe case: Questionable/No responses that are included. Yes responses that are excluded

A threshold of 6 fits splits the data well - lets look at fringe cases using a threshold of 4, 6, and 8

Threshold of 4:
```{r}
plot(G9202.32$time, G9202.32$dFF, type = "n", xlim = c(-8, 30), ylim = c(-0.5, 1.5), 
     main = "Fringe Cases: Z-score = 4", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.73, G9025.73$time), col = "azure4", lwd = 2)
lines(predict(ss.9023.12, G9023.12$time), col = "azure4", lwd = 2)
lines(predict(ss.9204.11, G9204.11$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9022.11, G9022.11$time), col = "deeppink", lwd = 2)
lines(predict(ss.9202.32, G9202.32$time), col = "deeppink", lwd = 2)
lines(predict(ss.9202.12, G9202.12$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9203.53, G9203.53$time), col = "deeppink", lwd = 2)
lines(predict(ss.9023.13, G9023.13$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9025.53, G9025.53$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9202.13, G9202.13$time), col = "darkgoldenrod", lwd = 2)
legend("topright", 
       legend = c("Yes Reference", "No Reference", 
                  "Questionable: 9204.11", "No: 9022.11", "No: G9202.32",
                  "Questionable: 9202.12", "No: 9203.53", "Questionable: 9023.13",
                  "Questionable: 9025.53", "Questionable: 9202.13"),
       fill = c("azure4", "azure4", "darkgoldenrod", "deeppink", "deeppink",
                "darkgoldenrod", "deeppink", "darkgoldenrod", "darkgoldenrod", "darkgoldenrod"))
legend("topleft", legend = c("Included", "Excluded"), lty = 1:2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
```

Threshold of 6

```{r}
plot(G9202.32$time, G9202.32$dFF, type = "n", xlim = c(-8, 30), ylim = c(-0.5, 1.5), 
     main = "Fringe Cases: Z-score = 6", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.73, G9025.73$time), col = "azure4", lwd = 2)
lines(predict(ss.9023.12, G9023.12$time), col = "azure4", lwd = 2)
lines(predict(ss.9025.53, G9025.53$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9202.13, G9202.13$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9203.53, G9203.53$time), col = "deeppink", lwd = 2)
lines(predict(ss.9023.13, G9023.13$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9025.51, G9025.51$time), col = "chartreuse4", lty = 2, lwd = 2)
legend("topright", 
       legend = c("Yes Reference", "No Reference", 
                  "Questionable: 9025.53", "Questionable: 9202.13", 
                  "No: G9203.53", "Questionable: 9023.13", "Yes: 9025.51"),
       fill = c("azure4", "azure4", "darkgoldenrod", "darkgoldenrod", "deeppink",
                "darkgoldenrod", "chartreuse4"))
legend("topleft", legend = c("Included", "Excluded"), lty = 1:2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
```

Threshold of 8

```{r}
plot(G9202.32$time, G9202.32$dFF, type = "n", xlim = c(-8, 30), ylim = c(-0.5, 1.5), 
     main = "Fringe Cases: Z-score = 8", 
     xlab = substitute(paste(bold('Time'))), ylab = substitute(paste(bold('dF/F'))))
lines(predict(ss.9025.73, G9025.73$time), col = "azure4", lwd = 2)
lines(predict(ss.9023.12, G9023.12$time), col = "azure4", lwd = 2)
lines(predict(ss.9025.53, G9025.53$time), col = "darkgoldenrod", lwd = 2)
lines(predict(ss.9025.51, G9025.51$time), col = "chartreuse4", lty = 2, lwd = 2)
lines(predict(ss.9025.74, G9025.74$time), col = "chartreuse4", lty = 2, lwd = 2)
lines(predict(ss.9025.14, G9025.14$time), col = "chartreuse4", lty = 2, lwd = 2)
legend("topright", 
       legend = c("Yes Reference", "No Reference","Questionable: 9025.53", "Yes: 9025.51", 
                  "Yes: 9025.74", "Yes: 9025.14"),
       fill = c("azure4", "azure4", "darkgoldenrod", "chartreuse4", "chartreuse4", "chartreuse4"))
legend("topleft", legend = c("Included", "Excluded"), lty = 1:2)
abline(a = 0, b = 0, h = 0, v = 0, lwd = 1)
```

Decided to go with a Z-score of 6 as our threshold for successful response - inclusive enough to capture some smaller or delayed responses that may occur as axons begin to regrow but not so inclusive that I'll miss classify a lot of failed responses.
