---
title: "Total Surface Area Uncut"
author: "Patrick"
date: "2023-11-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(data.table)
library(dplyr)
```
# 1) Surface Area Calculation Function

I asked bard to write me a function and provided it:

I ran an experiment in which I gathered data on many different subjects every two week for 24 weeks. Prior to that I gathered two weeks of baseline data: week -2 and week 0. I have a separate folder for each subject containing their raw data. Each of these folders contain an individual csv file for each corresponding week, labelled W-2, W0, W2, W4, W6, W8, W10, W12, W14, W16, W18, W20, W22, W24. Some subjects are missing certain weeks and therefore do not have a corresponding csv file. Each file contains 5 columns labeled: Area, Unit, Category, Time, ID. The header begins on row 4.

I have a data frame in R for each subject with the columns: animal, week, treatment, total.sa, new.sa, survived.sa, branched.sa, pre.sa.

I would like you to generate a function in R that loads the csv file for each subject’s weekly data, calculates the sum of the ‘Area’ column and then adds the following information to the subject’s data frame: week, total.sa. week is indicated in the name of the name of the csv file: W-2 should be entered as -2, W0 as 0, W2 as 2, etc. total.sa should be filled with the calculated sum. If no csv file exists, total.sa should be filled with NA.

The working directory will be set to subject’s folder and contain each csv file

Bard returned a function that retrieves total surface area from each CSV file within an animal's folder...well after som debugging:

```{r eval = FALSE}
# Input file path to subject folder
SA_calc <- function(subject_folder) {
    # Get the list of all CSV files in the subject's folder
    csv_files <- list.files(subject_folder)

    # Create a sequence of week numbers
    week_numbers <- seq(-2, 24, by = 2)
    
    # Iterate over the week numbers and add the data to the subject's data frame
    for (week_number in week_numbers) {
    # Check if the CSV file for the week exists
        csv_file <- paste0("W", week_number, ".csv")
        if (file.exists(file.path(subject_folder, csv_file))) {
            # If the CSV file exists, load it
            weekly_data <- read.csv(file.path(subject_folder, csv_file), skip = 3)
            
            # Calculate the sum of the 'Area' column
            total_sa <- sum(weekly_data$Area)
            
        } else {
        # If the CSV file does not exist, fill in the total.sa value with NA
            total_sa <- NA
        }
        
        # Add the week and total.sa values to the subject's data frame
        subject_data <- rbind(subject_data, data.frame(week = week_number, total.sa = total_sa))
    }
    
    # Iterate over the week numbers and calculate the normalized surface area
    for (i in 1:14) {
        subject_data$norm.total.sa <- subject_data$total.sa / subject_data$total.sa[2]
    }
    
    # Return the subject's data frame
    return(subject_data)
}
```

Lets see how it works:

```{r}
subject_data <- data.frame()
subject_folder <- "./Total Surface Area/9022"
subject_data <- SA_calc(subject_folder)
subject_data
```

OK that's great, I can run that on every animal and merge it into a dataframe for that animal and then a master frame

# 2) Assemble individual animal dataframes for total surface area

## 1) Figure it out

Lets create a data frame for 9022 and add in the calculation from above

```{r}
# Creates an empty data frame
A9022 <- data.frame()
# Adds 14 columns to facilitate individually adding data later
A9022[1:14, ] <- NA
A9022
```
Info for columns that are consistent between weeks
```{r}
# Fills animal column
animal <- rep("9022", times = 14)
animal
# Fills in sex column
sex <- rep("F", times = 14)
sex
# Fills week column
week <- seq(-2, 24, by = 2)
week
# Fills functional column identifying if the animal qualified for functional assessment
functional <- rep(TRUE, times = 14)
functional
# Will fill treatment column with treatment
treatment <- rep("treatment", times = 14)
treatment
# Will fill treatment column with control
control <- rep("control", times = 14)
control
# Fills group.id column identifying which cohort the animal was in.
group.id <- rep(1, times = 14)
group.id
```
Fill those consistent columns

```{r}
A9022$animal <- as.factor(animal)
A9022$sex <- as.factor(sex)
A9022$group <- as.factor(group.id)
A9022$functional <- functional
A9022$week <- week
# Input control or treatment accordingly
A9022$treatment <- as.factor(treatment)
A9022
```
Merges in the SA_calc results to animal's data frame

```{r}
A9022 <- full_join(A9022, subject_data, by = "week", copy = TRUE)
A9022
```

# 3) Fill total.sa column for each animal
## 9022
```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9022"
subject_data <- SA_calc(subject_folder)
# Change object name
A9022 <- data.frame()
# Change object name
A9022[1:14, ] <- NA
# Assign animal number
animal <- rep("9022", times = 14)
# Assign sex
sex <- rep("M", times = 14)
# Assign group
group.id <- rep(1, times = 14)
# Function, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9022$animal <- as.factor(animal)
# Change object name
A9022$sex <- as.factor(sex)
# Change object name
A9022$group.id <- as.factor(group.id)
# change object name
A9022$functional <- functional
# Change object name
A9022$week <- week
# Change object name and input treatment/control
A9022$treatment <- as.factor(treatment)
# Change object name TWICE
A9022 <- full_join(A9022, subject_data, by = "week", copy = TRUE)
# Change object name
A9022
```
## 9023

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9023"
subject_data <- SA_calc(subject_folder)
# Change object name
A9023 <- data.frame()
# Change object name
A9023[1:14, ] <- NA
# Assign animal number
animal <- rep("9023", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(1, times = 14)
# Function, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9023$animal <- as.factor(animal)
# Change object name
A9023$sex <- as.factor(sex)
# Change object name
A9023$group.id <- as.factor(group.id)
# change object name
A9023$functional <- functional
# Change object name
A9023$week <- week
# Change object name and input treatment/control
A9023$treatment <- as.factor(control)
# Change object name TWICE
A9023 <- full_join(A9023, subject_data, by = "week", copy = TRUE)
# Change object name
A9023
```

## 9025
```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9025"
subject_data <- SA_calc(subject_folder)
# Change object name
A9025 <- data.frame()
# Change object name
A9025[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9025", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(1, times = 14)
# Function, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9025$animal <- as.factor(animal)
# Change object name
A9025$sex <- as.factor(sex)
# Change object name
A9025$group.id <- as.factor(group.id)
# Change object name
A9025$functional <- functional
# Change object name
A9025$week <- week
# # Change object name and input treatment/control
A9025$treatment <- as.factor(control)
# Change object name TWICE
A9025 <- full_join(A9025, subject_data, by = "week", copy = TRUE)
# Change object name
A9025
```
## 9026

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9026"
subject_data <- SA_calc(subject_folder)
# Change object name
A9026 <- data.frame()
# Change object name
A9026[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9026", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(1, times = 14)
# Function, TRUE or FALSE?
functional <- rep(FALSE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9026$animal <- as.factor(animal)
# Change object name
A9026$sex <- as.factor(sex)
# Change object name
A9026$group.id <- as.factor(group.id)
# Change object name
A9026$functional <- functional
# Change object name
A9026$week <- week
# # Change object name and input treatment/control
A9026$treatment <- as.factor(treatment)
# Change object name TWICE
A9026 <- full_join(A9026, subject_data, by = "week", copy = TRUE)
# Change object name
A9026
```

## 9031
```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9031"
subject_data <- SA_calc(subject_folder)
# Change object name
A9031 <- data.frame()
# Change object name
A9031[1:14, ] <- NA
# Change animal ID
animal <- rep("9031", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(1, times = 14)
# Function, TRUE or FALSE?
functional <- rep(FALSE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9031$animal <- as.factor(animal)
# Change object name
A9031$sex <- as.factor(sex)
# Change object name
A9031$group.id <- as.factor(group.id)
# Change object name
A9031$functional <- functional
# Change object name
A9031$week <- week
# Change object name and input treatment/control
A9031$treatment <- as.factor(treatment)
# Change object name TWICE
A9031 <- full_join(A9031, subject_data, by = "week", copy = TRUE)
# Change object name
A9031
```
## 9035

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9035"
subject_data <- SA_calc(subject_folder)
# Change object name
A9035 <- data.frame()
# Change object name
A9035[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9035", times = 14)
# Assign sex
sex <- rep("M", times = 14)
# Assign group
group.id <- rep(1, times = 14)
# Function, TRUE or FALSE?
functional <- rep(FALSE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9035$animal <- as.factor(animal)
# Change object name
A9035$sex <- as.factor(sex)
# Change object name
A9035$group.id <- as.factor(group.id)
# Change object name
A9035$functional <- functional
# Change object name
A9035$week <- week
# Change object name and input treatment/control
A9035$treatment <- as.factor(control)
# Change object name TWICE
A9035 <- full_join(A9035, subject_data, by = "week", copy = TRUE)
# Change object name
A9035
```

## 9058

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9058"
subject_data <- SA_calc(subject_folder)
# Change object name
A9058 <- data.frame()
# Change object name
A9058[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9058", times = 14)
# Assign sex
sex <- rep("M", times = 14)
# Assign group
group.id <- rep(4, times = 14)
# Function, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9058$animal <- as.factor(animal)
# Change object name
A9058$sex <- as.factor(sex)
# Change object name
A9058$group.id <- as.factor(group.id)
# Change object name
A9058$functional <- functional
# Change object name
A9058$week <- week
# Change object name and input treatment/control
A9058$treatment <- as.factor(treatment)
# Change object name TWICE
A9058 <- full_join(A9058, subject_data, by = "week", copy = TRUE)
# Change object name
A9058
```

## 9060

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9060"
subject_data <- SA_calc(subject_folder)
# Change object name
A9060 <- data.frame()
# Change object name
A9060[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9060", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(4, times = 14)
# Function, TRUE or FALSE?
functional <- rep(FALSE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9060$animal <- as.factor(animal)
# Change object name
A9060$sex <- as.factor(sex)
# Change object name
A9060$group.id <- as.factor(group.id)
# Change object name
A9060$functional <- functional
# Change object name
A9060$week <- week
# Change object name and input treatment/control
A9060$treatment <- as.factor(control)
# Change object name TWICE
A9060 <- full_join(A9060, subject_data, by = "week", copy = TRUE)
# Change object name
A9060
```

## 9062

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9062"
subject_data <- SA_calc(subject_folder)
# Change object name
A9062 <- data.frame()
# Change object name
A9062[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9062", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(4, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9062$animal <- as.factor(animal)
# Change object name
A9062$sex <- as.factor(sex)
# Change object name
A9062$group.id <- as.factor(group.id)
# Change object name
A9062$functional <- functional
# Change object name
A9062$week <- week
# Change object name and input treatment/control
A9062$treatment <- as.factor(treatment)
# Change object name TWICE
A9062 <- full_join(A9062, subject_data, by = "week", copy = TRUE)
# Change object name
A9062
```

## 9067

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9067"
subject_data <- SA_calc(subject_folder)
# Change object name
A9067 <- data.frame()
# Change object name
A9067[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9067", times = 14)
# Assign sex
sex <- rep("M", times = 14)
# Assign group
group.id <- rep(4, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9067$animal <- as.factor(animal)
# Change object name
A9067$sex <- as.factor(sex)
# Change object name
A9067$group.id <- as.factor(group.id)
# Change object name
A9067$functional <- functional
# Change object name
A9067$week <- week
# Change object name and input treatment/control
A9067$treatment <- as.factor(control)
# Change object name TWICE
A9067 <- full_join(A9067, subject_data, by = "week", copy = TRUE)
# Change object name
A9067
```

## 9068

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9068"
subject_data <- SA_calc(subject_folder)
# Change object name
A9068 <- data.frame()
# Change object name
A9068[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9062", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(5, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9068$animal <- as.factor(animal)
# Change object name
A9068$sex <- as.factor(sex)
# Change object name
A9068$group.id <- as.factor(group.id)
# Change object name
A9068$functional <- functional
# Change object name
A9068$week <- week
# Change object name and input treatment/control
A9068$treatment <- as.factor(treatment)
# Change object name TWICE
A9068 <- full_join(A9068, subject_data, by = "week", copy = TRUE)
# Change object name
A9068
```

## 9071

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9071"
subject_data <- SA_calc(subject_folder)
# Change object name
A9071 <- data.frame()
# Change object name
A9071[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9071", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(5, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(FALSE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9071$animal <- as.factor(animal)
# Change object name
A9071$sex <- as.factor(sex)
# Change object name
A9071$group.id <- as.factor(group.id)
# Change object name
A9071$functional <- functional
# Change object name
A9071$week <- week
# Change object name and input treatment/control
A9071$treatment <- as.factor(control)
# Change object name TWICE
A9071 <- full_join(A9071, subject_data, by = "week", copy = TRUE)
# Change object name
A9071
```

## 9072

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9072"
subject_data <- SA_calc(subject_folder)
# Change object name
A9072 <- data.frame()
# Change object name
A9072[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9072", times = 14)
# Assign sex
sex <- rep("M", times = 14)
# Assign group
group.id <- rep(5, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9072$animal <- as.factor(animal)
# Change object name
A9072$sex <- as.factor(sex)
# Change object name
A9072$group.id <- as.factor(group.id)
# Change object name
A9072$functional <- functional
# Change object name
A9072$week <- week
# Change object name and input treatment/control
A9072$treatment <- as.factor(control)
# Change object name TWICE
A9072 <- full_join(A9072, subject_data, by = "week", copy = TRUE)
# Change object name
A9072
```

## 9073

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9073"
subject_data <- SA_calc(subject_folder)
# Change object name
A9073 <- data.frame()
# Change object name
A9073[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9073", times = 14)
# Assign sex
sex <- rep("M", times = 14)
# Assign group
group.id <- rep(5, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(FALSE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9073$animal <- as.factor(animal)
# Change object name
A9073$sex <- as.factor(sex)
# Change object name
A9073$group.id <- as.factor(group.id)
# Change object name
A9073$functional <- functional
# Change object name
A9073$week <- week
# Change object name and input treatment/control
A9073$treatment <- as.factor(treatment)
# Change object name TWICE
A9073 <- full_join(A9073, subject_data, by = "week", copy = TRUE)
# Change object name
A9073
```

## 9202

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9202"
subject_data <- SA_calc(subject_folder)
# Change object name
A9202 <- data.frame()
# Change object name
A9202[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9202", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(3, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9202$animal <- as.factor(animal)
# Change object name
A9202$sex <- as.factor(sex)
# Change object name
A9202$group.id <- as.factor(group.id)
# Change object name
A9202$functional <- functional
# Change object name
A9202$week <- week
# Change object name and input treatment/control
A9202$treatment <- as.factor(treatment)
# Change object name TWICE
A9202 <- full_join(A9202, subject_data, by = "week", copy = TRUE)
# Change object name
A9202
```

## 9203

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9203"
subject_data <- SA_calc(subject_folder)
# Change object name
A9203 <- data.frame()
# Change object name
A9203[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9203", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(3, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9203$animal <- as.factor(animal)
# Change object name
A9203$sex <- as.factor(sex)
# Change object name
A9203$group.id <- as.factor(group.id)
# Change object name
A9203$functional <- functional
# Change object name
A9203$week <- week
# Change object name and input treatment/control
A9203$treatment <- as.factor(control)
# Change object name TWICE
A9203 <- full_join(A9203, subject_data, by = "week", copy = TRUE)
# Change object name
A9203
```

## 9204

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9204"
subject_data <- SA_calc(subject_folder)
# Change object name
A9204 <- data.frame()
# Change object name
A9204[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9204", times = 14)
# Assign sex
sex <- rep("M", times = 14)
# Assign group
group.id <- rep(3, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9204$animal <- as.factor(animal)
# Change object name
A9204$sex <- as.factor(sex)
# Change object name
A9204$group.id <- as.factor(group.id)
# Change object name
A9204$functional <- functional
# Change object name
A9204$week <- week
# Change object name and input treatment/control
A9204$treatment <- as.factor(control)
# Change object name TWICE
A9204 <- full_join(A9204, subject_data, by = "week", copy = TRUE)
# Change object name
A9204
```

## 9211

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9211"
subject_data <- SA_calc(subject_folder)
# Change object name
A9211 <- data.frame()
# Change object name
A9211[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9211", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(6, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9211$animal <- as.factor(animal)
# Change object name
A9211$sex <- as.factor(sex)
# Change object name
A9211$group.id <- as.factor(group.id)
# Change object name
A9211$functional <- functional
# Change object name
A9211$week <- week
# Change object name and input treatment/control
A9211$treatment <- as.factor(treatment)
# Change object name TWICE
A9211 <- full_join(A9211, subject_data, by = "week", copy = TRUE)
# Change object name
A9211
```

## 9212

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9212"
subject_data <- SA_calc(subject_folder)
# Change object name
A9212 <- data.frame()
# Change object name
A9212[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9212", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(6, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9212$animal <- as.factor(animal)
# Change object name
A9212$sex <- as.factor(sex)
# Change object name
A9212$group.id <- as.factor(group.id)
# Change object name
A9212$functional <- functional
# Change object name
A9212$week <- week
# Change object name and input treatment/control
A9212$treatment <- as.factor(control)
# Change object name TWICE
A9212 <- full_join(A9212, subject_data, by = "week", copy = TRUE)
# Change object name
A9212
```

## 9213

```{r}
subject_data <- data.frame()
# Input the correct file path
subject_folder <- "./Total Surface Area/9213"
subject_data <- SA_calc(subject_folder)
# Change object name
A9213 <- data.frame()
# Change object name
A9213[1:14, ] <- NA
# Modify animal according to subject number
animal <- rep("9213", times = 14)
# Assign sex
sex <- rep("F", times = 14)
# Assign group
group.id <- rep(6, times = 14)
# Functional, TRUE or FALSE?
functional <- rep(TRUE, times = 14)
week <- seq(-2, 24, by = 2)
treatment <- rep("treatment", times = 14)
control <- rep("control", times = 14)
# Change object name
A9213$animal <- as.factor(animal)
# Change object name
A9213$sex <- as.factor(sex)
# Change object name
A9213$group.id <- as.factor(group.id)
# Change object name
A9213$functional <- functional
# Change object name
A9213$week <- week
# Change object name and input treatment/control
A9213$treatment <- as.factor(treatment)
# Change object name TWICE
A9213 <- full_join(A9213, subject_data, by = "week", copy = TRUE)
# Change object name
A9213
```

# Final step: merge all data frames together

```{r}
# list of all the data frames to be combined
structural_master <- rbind.data.frame(A9022, A9023, A9025, A9026, A9031, A9035,
                    A9058, A9060, A9062, A9067,
                    A9068, A9071, A9072, A9073,
                    A9202, A9203, A9204,
                    A9211, A9212, A9213)
structural_master
```

```{r}
A9072
```
















